Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-31 sections/results.tex
sum the number of unclear set.

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 60, 51, and 122 for useless set (\texttt{YES} = 0), unclear set (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

>>>>

\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively. The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
